\section{Non-Euclidean geometry}

The \textit{Euclidean} geometry is based on a set of five postulates originally given by Euclid.
The postulates read as follows \cite{Weisstein-Postulates}:
\begin{enumerate}
    \item A straight line segment can be drawn joining any two points.
    \item Any straight line segment can be extended indefinitely in a straight line.
    \item Given any straight line segment, a circle can be drawn having the segment as the radius and one endpoint as the center.
    \item All right angles are congruent.
    \item Given any straight line and a point not on it, there exists one and only one straight line that passes through that point and never intersects the first line, no matter how far they are extended. \cite{Weisstein-Parallel}
\end{enumerate}
The fifth postulate, also called the \textit{parallel postulate}, has been for hundreds of years a subject of debate if it can be proven from the former four postulates.
It was discovered, however, that the negation of the parallel postulate doesn't lead to a contradiction\cite{Parallel-Postulate}.
The postulate can be negated in one of two ways.
\begin{itemize}
    \item Given any straight line and a point not on it, there exist \textbf{at least two straight lines} that pass through that point and never intersect the first line, no matter how far they are extended.
    \item Given any straight line and a point not on it, there exists \textbf{no straight line} that passes through that point and never intersects the first line; in other words, there are no parallel lines, since any two lines must intersect.
\end{itemize}

When the parallel postulate is replaced with the first statement, we obtain a new geometry, called the \textit{hyperbolic geometry}.
Similarly, replacing it with the second statement yields the \textit{spherical geometry}.
These geometries are collectively referred to as \textit{non-Euclidean geometries}.

\input{chapters/theoretical_foundations/sections/non-eudlidean-spaces/subsections/analytic_description.tex}
\input{chapters/theoretical_foundations/sections/non-eudlidean-spaces/subsections/transformations.tex}
\input{chapters/theoretical_foundations/sections/non-eudlidean-spaces/subsections/practical_considerations.tex}